State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2015-10-29 draft.tex
Daily changes.
what happened

[ticket: X]

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{hroughout} this paper we denote by $f\vert_{\mathcal C} = \{y:\exists x\in\mathcal C\;y=f(x)\}$
the image of $\mathcal C$ under the map $f$, for polytopes defined by intersection of the halfspaces 
$a_i x \leq b_i$ for $i\in\{1,\dots,m\}$ we denote the matrix~${\bf{a}}_{\mathcal I}$ and vector~
${\bf{b}}_{\mathcal I}$ with the rows $a_i$ and $b_i$ for all indices in the index set $i\in\mathcal 
I\subseteq\{1,\dots,m\}$.

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.

Robust model predictive control (RMPC) methods compute control laws for uncertain systems that optimise a 
performance criterion for all possible realisations of the uncertainties.
%
One major challenge in RMPC is to guarantee feasibility of the problem for all possible uncertainties in 
presence of state constraints.
%
This can be achieved by introducing specifically designed constraints in such a way that at the
end of the control horizon the system state is contained in a set that is feasible and invariant for all
possible realisations of uncertainty and for a given feedback controller, in particular the largest such set, 
the so called \emph{maximal robust positive invariant} (MRPI) set.
%
Although this concept was introduced shortly after Witsenhausen proposed the use of a game theoretic approach
to robust model predictive control in~\cite{Witsenhausen:1968} by several authors~\cite{Bertsekas:1971,Glover:1971},
it took over two decades before the first MRPI sets could be algorithmically determined.

Throughout this paper we denote by $f\vert_{\mathcal C} = \{y:\exists x\in\mathcal C\;y=f(x)\}$
the image of $\mathcal C$ under the map $f$, for polytopes defined by intersection of the halfspaces 
$a_i x \leq b_i$ for $i\in\{1,\dots,m\}$ we denote the matrix~${\bf{a}}_{\mathcal I}$ and vector~
${\bf{b}}_{\mathcal I}$ with the rows $a_i$ and $b_i$ for all indices in the index set $i\in\mathcal 
I\subseteq\{1,\dots,m\}$.
